Supplementary material S5: Biodiversity effect results

### 2018-11-06 S4-LM.Rmd
# Draft 0.1.9007 * Fourth version after @BrunoHerault meeting

---
title: "Supplementary material S4: Linear models"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

```{r Ir, cache=TRUE, echo=FALSE}
Ir <- Deq %>% 
  group_by(sim) %>% 
  arrange(time) %>% 
  mutate_at(vars(-time), cumsum) %>% 
  filter(time == 600)
```

This supplementary materials is here check the validity of the linear model and to give additional ouptuts of the results not shown in the manuscript. It will be separated in three parts, (i) linear models, (ii) variables multicolinearity, (iii) validation of linear models, and (iii) results of linear models.

@@

We want to test the effect of diversity on the resilience indice $I_R$. For that we will two models, one including only multi-trait diversity indices (model \@ref(eq:m1)) and one including single-trait diversity indices (model \@ref(eq:m2)):

@@

This results in 2 models multiplied by 11 $I_R$ indices giving 22 regressions.

@@

We tested multicolinearity for all variables from the two models, and none of theim have shown multicolinearity issues (see figure \@ref(fig:multicolinearity)).

```{r multicolinearity, fig.cap="Pairs plot and multicolinearity between diversity indices."}
doe %>% 
  select(SR, FEve, FDiv, FDis.LMA, FDis.wsg, FDis.hmax) %>% 
  GGally::ggpairs()
```

@@

We validated the 66 regressions with diagnostic plots (qqplot and Cook's leverage). Figures \@ref(fig:diag1Str), \@ref(fig:diag1Prod), \@ref(fig:diag2Str) and \@ref(fig:diag2Prod) shows relations between the $I_R$ indices for several ecosystem outputs and diversity indices. Most of theim did not seems to have issues. Still $n$, $n10$ and $n30$ showed strong outliers for every level of disturbance and disturbance intensity of 75% included those outliers in the $structure$ output. Similarly disturbance intensity of 75% included outliers for $production$, $gpp$, $npp$, $Rday$ and $Rnight$. Those outliers are linked to species with only 5 species strongly disturbed that might derived through an unexpected ecosystem state. Nevertheless those outliers hsould be taken into account in further interpretations.

@@

```{r diag1Str, fig.cap="Effect of multi-trait diversity indices on resilience index $I_R$ for ecosystem variables linked to structure (AGB, BA, N, N10 and N30)."}
Ir %>% 
  left_join(doe, by = "sim") %>% 
  ungroup() %>% 
  select(disturbance, 
         structure, agb, ba, n, n10, n30,
         SR, FEve, FDiv) %>% 
  reshape2::melt(id.vars = c("disturbance", "SR", "FEve", "FDiv"), value.name = "Ir") %>% 
  ggplot(aes(FDiv, Ir, shape = SR, col = FEve, group = NA)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(disturbance~variable, scales = "free_y", nrow = 3)
```

@@

@@

@@

@@

Globally and as expected, $structure$ variables represents well $AGB$, $BA$, $N$, $N10$, with a strong negative effect of functional diversity $FDiv$ increasing with disturbance intensity and a significative effect of functional eveness $FEve$ only for the strongest distruabnce of 75%. $N30$ did not had any significant effect from diversity indices in multitrait. $SR25$ decreased $I_R$ for strong disturbance, only through its significative but low effect on $BA$.

Similarly, $production$ variable represented well $GPP$, $NPP$, $Rday$ and $Rnight$ with a significant effect of both functional diversity $FDiv$ and eveness $FEve$ increasing with all disturbance levels (except $FDiv$ for a disturbance of 75%). $SR25$ decreased $I_R$ for strong disturbance, only through its significative but low effect on $NPP$.

@@

Globally mono-trait functional dispersion indices did not changed a lot the result due to absent or weak effects. Regarding $structure$, $FDis.hmax$ and $FDis.wsg$ had respectivelly significant small positive and negative effects on $BA$ and $N10$ but not on $structure$ itself, except for $FDis.wsg$ at low disturbance intensity (25%). On the opposite for $production$, $FDis.LMA$ had a significant positive effect increasing with disturbance intensity on $production$, $npp$, $Rday$ and $Rnight$.

@@

@@

We developped here two linear models to explore the result of our simulations and more particularly the linked between diversity indices and resilience of ecosystem variables. Our main issues is to summarize the global information of the 66 regressions in something more easy to assimilate for the reader.

First, I think that based on the hysteresis issue we can justify and use the aggregated variables $structure$ and $production$ to summarize all ecosystem variables. And I prefer to show and interpret those general ones, even if they are more abstrait, instead of picking one as an example.

Secondly, for $structure$ and $production$ variables models \@ref(eq:m1) and \@ref(eq:m2) gives similar results, at the exception of the effect of $FDis.LMA$ in $production$ resilience. So I think we can keep only model \@ref(eq:m2) keeping in mind the effect of $FDis.LMA$ on $production$.

>>>>

---
title: "Supplementary material S4: Linear models"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::word_document2: default
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

```{r Ir, cache=TRUE, echo=FALSE}
Ir <- Deq %>% 
  group_by(sim) %>% 
  arrange(time) %>% 
  mutate_at(vars(-time, -sim), cumsum) %>% 
  filter(time == 600)
```

This supplementary material is here to check the validity of the linear model and to give additional ouptuts of the results not shown in the manuscript. It will be separated in four parts, (i) linear models, (ii) variables multicolinearity, (iii) validation of linear models, and (iv) results of linear models.

@@

We want to test the effect of diversity on the resilience indice $I_R$. For that we will test two models, one including only multi-trait diversity indices (model \@ref(eq:m1)) and one including single-trait diversity indices (model \@ref(eq:m2)):

@@

This results in two models multiplied by 11 $I_R$ indices giving 22 regressions.

@@

We tested multicolinearity for all independent variables of the two models, and none of theim have shown multicolinearity issues (all Pearson's and/or Spearman's correlation coefficients below 0.6, see figure \@ref(fig:multicolinearity)).

```{r multicolinearity, fig.cap="Pairs plot and multicolinearity between diversity indices. Subplots lower the diagonal shows scatterplots between continuous variables or boxplot when a discrete variable is implied. Subplots on the diagonal show density plot for continuous variables and barplot for discrete variables. Subplots upper the diagonal indicates the Pearson's correlation coefficient between variables."}
doe %>% 
  select(SR, FEve, FDiv, FDis.LMA, FDis.wsg, FDis.hmax) %>% 
  GGally::ggpairs()
```

@@

We validated the 66 regressions with diagnostic plots (qqplot and Cook's leverage). Figures \@ref(fig:diag1Str), \@ref(fig:diag1Prod), \@ref(fig:diag2Str) and \@ref(fig:diag2Prod) shows relations between the $I_R$ indices computed for several ecosystem outputs, and diversity indices. Most of theim met the model assumptions requirements. Still $n$, $n10$ and $n30$ showed strong outliers for every level of disturbance in the two models. Those outliers echoed in the $structure$ variable only at a disturbance intensity of 75%. Similarly disturbance intensity of 75% included outliers for $production$, $gpp$, $npp$, $Rday$ and $Rnight$. Previously identified outliers corresponded to ecosystem simulations with only 5 species, which seemed to have derived toward an unexpected ecosystem state when strongly disturbed. Nevertheless those outliers should be taken into account in further interpretations.

## Multitrait

@@

```{r diag1Str, fig.cap="Effect of multi-trait diversity indices on resilience index $I_R$ for ecosystem variables linked to structure (AGB, BA, N, N10 and N30). To be completed with significativity and regression outputs when the final figure is chosen."}
Ir %>% 
  left_join(doe, by = "sim") %>% 
  ungroup() %>% 
  select(disturbance, 
         structure, agb, ba, n, n10, n30,
         SR, FEve, FDiv) %>% 
  reshape2::melt(id.vars = c("disturbance", "SR", "FEve", "FDiv"), value.name = "Ir") %>% 
  ggplot(aes(FDiv, Ir, shape = SR, col = FEve, group = NA)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(disturbance~variable, scales = "free_y", nrow = 3)
```

@@

## Monotrait

@@

#### FM

```{r diag3Str, fig.cap="Effect of mono-trait diversity indices on resilience index $I_R$ for structure ecosystem variables."}
Ir %>% 
  left_join(doe, by = "sim") %>% 
  ungroup() %>% 
  select(disturbance, 
         structure,
         CWM.LMA, CWM.wsg, CWM.hmax) %>% 
  reshape2::melt(id.vars = c("disturbance", "structure"), 
                 value.name = "CWM", variable.name = "Trait") %>% 
  ggplot(aes(CWM, structure, group = NA)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(disturbance~Trait, scales = "free", nrow = 3)
```

#### FD

@@

#### FM

```{r diag3Prod, fig.cap="Effect of mono-trait diversity indices on resilience index $I_R$ for production ecosystem variables."}
Ir %>% 
  left_join(doe, by = "sim") %>% 
  ungroup() %>% 
  select(disturbance, 
         production,
         CWM.LMA, CWM.wsg, CWM.hmax) %>% 
  reshape2::melt(id.vars = c("disturbance", "production"), 
                 value.name = "CWM", variable.name = "Trait") %>% 
  ggplot(aes(CWM, production, group = NA)) +
  geom_smooth(method = "lm") +
  geom_point() +
  facet_wrap(disturbance~Trait, scales = "free", nrow = 3)
```

#### FD

@@

Globally and as expected, $structure$ variables represented well $AGB$, $BA$, $N$ and $N10$ behavior, with a strong negative effect of functional diversity $FDiv$ on $I_r$ increasing with disturbance intensity and a significative effect of functional eveness $FEve$ only for the strongest distruabnce of 75%. $N30$ did not had any significant effect from diversity indices in multitrait. $SR25$ decreased $I_R$ for strong disturbance, only through its significative but low effect on $BA$.

Similarly, $production$ variable represented well $GPP$, $NPP$, $Rday$ and $Rnight$ behavior, with a significant effect of both functional diversity $FDiv$ and eveness $FEve$ on $I_r$ increasing with all disturbance levels (except $FDiv$ for a disturbance of 75%). $SR25$ decreased $I_R$ for strong disturbance, only through its significative but low effect on $NPP$.

@@

Globally mono-trait functional dispersion indices did not changed a lot the result due to absent or weak effects. Regarding $structure$, $FDis.hmax$ and $FDis.wsg$ had respectivelly significant small positive and negative effects on $BA$ and $N10$ but not on $structure$ itself, except for $FDis.wsg$ at low disturbance intensity (25%). On the opposite for $production$, $FDis.LMA$ had a significant positive effect increasing with disturbance intensity on $production$, $npp$, $Rday$ and $Rnight$. Increased dispersion in LMA traits thus tend to decrease ecosystem resilience of production variables.

@@

## Monotrait only

Adding $FM$  as the weighted sum of species traits = $CWM$.

```{r fit3}
Ir %>% 
  left_join(doe, by = "sim") %>% 
  ungroup() %>% 
  select(disturbance, 
         structure, agb, ba, n, n10, n30,
         production, gpp, npp, Rday, Rnight,
         SR, FDis.LMA, FDis.wsg, FDis.hmax,
         CWM.LMA, CWM.wsg, CWM.hmax) %>% 
  reshape2::melt(id.vars = c("disturbance", "SR", 
                             "FDis.LMA", "FDis.wsg", "FDis.hmax",
                             "CWM.LMA", "CWM.wsg", "CWM.hmax"), value.name = "Ir") %>% 
  group_by(variable, disturbance) %>%
  do(fit = lm(Ir ~ SR + CWM.LMA + CWM.wsg + CWM.hmax + FDis.LMA + FDis.wsg + FDis.hmax, data = .)) %>% 
  tidy(fit) %>% 
  ungroup() %>% 
  filter(term != "(Intercept)") %>% 
  mutate(`P-value` = ifelse(p.value < 0.001, "***",
                       ifelse(p.value < 0.01, "**",
                              ifelse(p.value < 0.05, "*",
                                     ifelse(p.value < 0.1, ".", "n.s."))))) %>% 
  mutate(Coefficient = round(estimate,2)) %>% 
  mutate(Recovery = variable) %>% 
  rename(Variable = term, `Disturbance intensity` = disturbance) %>%
  select(Recovery, `Disturbance intensity`, Variable, Coefficient, `P-value`) %>%
  mutate(value = paste(Coefficient, `P-value`)) %>% 
  mutate(value = cell_spec(value, 
                           bold = ifelse(grepl("*", value, fixed = T), T, F))) %>%
  reshape2::dcast(Recovery + `Disturbance intensity` ~ Variable, value.var = "value") %>% 
  kable(caption = "Result of linear regression testing the effect of species richness and functional diversity indices on the recovery index by recovery type and disturbance intensity.", escape = F) %>% 
  kable_styling(full_width = F) %>% 
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2)
```

@@

We developped here two linear models to explore the result of our simulations and more particularly the links between diversity indices and resilience of ecosystem variables. Our main issues is to summarize the global information of the 66 regressions in something more easy to assimilate for the reader.

First, I think that based on the hysteresis issue, the fact that ecosystem variables can reach equilibrium value in a transient state whithout reaching equilibirum, we can justify and use the aggregated variables $structure$ and $production$ to summarize all ecosystem variables. And I prefer to show and interpret those general ones, even if they are more abstrait, instead of picking one as an example.

Secondly, for $structure$ and $production$ variables models \@ref(eq:m1) and \@ref(eq:m2) gives similar results, at the exception of the effect of $FDis.LMA$ in $production$ resilience, meaning that in most of the case monotrait information is not useful. So I think we can keep only model \@ref(eq:m2) keeping in mind the effect of $FDis.LMA$ on $production$.

### 2018-11-06 S5-Biodiversity.Rmd
# Draft 0.1.9007 * Fourth version after @BrunoHerault meeting

---
title: "Supplementary material S5: Biodiversity effect results"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

This document explore graphically the result of the biodiversity net effect partitionning. More especially we want to look if the representation from figure \@ref(fig:gBE) is correct, with the dynamic biodiversity net effect normalized by the control across ecosystems. In order to do that we will start by looking into the dynamic of a single ecosystem \@ref(fig:gBEsingle), we will then move to all ecosystem not normalized by the control \@ref(fig:gBEunorm), before validating our current representation \@ref(fig:gBE).

@@

The net effect of biodiversity on ecosystem recovery was partitioned between selection and complementarity effect. We are thus able for one community to look at aboveground biomass dynamic after and before disturbance in control and disturbed ecosystems and correspondig bioviersity net effect, selection effect and complementarity effect (figure \@ref(fig:gBEsingle)). Similarly to global aboveground biomass from the ecosystem the biodiversity net effect and selection effect decrease following the disturbance, whereas the complementarity effect directly increase following the disturbance. Interestingly, we can see that this pattern of decrease of selection effect after disturbance and recovery after is similar to the effect of succession in forest early stages (first century, sub-figure on left-bottom on figure \@ref(fig:gBEsingle)).

```{r gBEsingle, fig.cap='Dynamic of complementarity and selection effects before and after the disturbance event for one ecosystem including 125 species. Solid lines represents the mean value whereas areas represents the interval of values among simulations.'}
g <- BE %>% 
  select(sim, BE, time, agb) %>% 
  separate(sim, c("SR", "CHV", "disturbance"), remove = F) %>% 
  rbind(ecosystem %>% 
          mutate(BE = "ecosystem") %>%
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV", "disturbance"), remove = F)) %>% 
  rbind(BE_mature %>% 
          mutate(time = time - 600) %>% 
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV"), remove = F) %>% 
          mutate(disturbance = "0-75") %>% 
          separate_rows(disturbance, sep = "-", convert = T)) %>% 
  rbind(mature %>% 
          mutate(time = time-600) %>% 
          mutate(BE = "ecosystem") %>% 
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV"), remove = F) %>% 
          mutate(disturbance = "0-75") %>% 
          separate_rows(disturbance, sep = "-", convert = T)) %>% 
  filter(SR == 125, disturbance %in% c(0,75), CHV == 4) %>% 
  reshape2::dcast(SR + CHV + BE + time ~ disturbance, value.var = "agb") %>% 
  rename(control = `0`, disturbed = `75`) %>% 
  ggplot(aes(x = time, col = BE, group = BE)) +
  geom_line(aes(y = control, linetype = "control")) +
  geom_line(aes(y = disturbed, linetype = "disturbed")) + 
  xlab("Time (years)") + 
  ylab("Aboveground biomass (tonC/ha)") +
  scale_color_discrete("Biodiversity\neffect")
g0 <- g + 
  geom_line(aes(y = control, linetype = "control")) +
  geom_line(aes(y = disturbed, linetype = "disturbed")) + 
  geom_ribbon(aes(ymin = disturbed, ymax = control), 
              col = NA, fill = "lightgrey", alpha = 0.5)
gdist <- g + 
  geom_line(aes(y = control, linetype = "control"), lwd = 1.4) +
  geom_line(aes(y = disturbed, linetype = "disturbed"), lwd = 1.4) + 
  xlim(-10,50) + ylim(NA, 60000) +
  scale_color_discrete(guide = F) +
  scale_linetype_discrete(guide = F)
gstart <- g + 
  geom_line(aes(y = control, linetype = "control"), lwd = 1.4) +
  geom_line(aes(y = disturbed, linetype = "disturbed"), lwd = 1.4) + 
  xlim(-600,-500) + ylim(NA, 50000) +
  scale_color_discrete(guide = F) +
  scale_linetype_discrete(guide = F)
gridExtra::grid.arrange(g0, gstart, gdist, 
                        layout_matrix = rbind(c(1, 1), c(2, 3)))
```

@@

If we aggregate the result of all community with 125 species, we still observe the same pattern (figure \@ref(fig:gBEunorm)). But due to an increase of biodiversity net effect through recovery time, complementarity importance in early recovery is less visible over a long period. Consequently normalizing by control biodiversity net effect can help avoiding this issue.

```{r gBEunorm, fig.cap='Dynamic of complementarity and selection effects for all ecosystems including 125 species. Solid lines represents the mean value whereas areas represents the interval of values among simulations.'}
BE %>% 
  rbind(mutate(ecosystem, BE = "ecosystem")) %>% 
  left_join(., doe, by = 'sim') %>%
  filter(SR == 125, disturbance == 75) %>% 
  group_by(time, BE, disturbance, SR) %>%
  summarise(qt1 =quantile(agb, probs=0.05),
            qt2 =quantile(agb, probs=0.75),
            mean=mean(agb),
            n=n()) %>% 
  ggplot(aes(x = time)) +
  geom_ribbon(aes(ymin = qt1, ymax = qt2, fill = BE), alpha = 0.3) +
  geom_line(aes(y = mean, color = BE)) +
  xlab('Time (years)') +
  ylab('Aboveground biomass net effect')
```

>>>>

---
title: "Supplementary material S5: Biodiversity effect results"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::word_document2: default
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

@@

This document explores graphically the result of the biodiversity net effect partitionning. More especially we want to look if the representation from figure \@ref(fig:gBE) is correct, with the dynamic biodiversity net effect normalized by the control across ecosystems. In order to do so, we will start by looking into the dynamics of a single ecosystem \@ref(fig:gBEsingle), we will then move to all ecosystems not normalized by the control \@ref(fig:gBEunorm), before validating our current representation \@ref(fig:gBE).

@@

The net effect of biodiversity on ecosystem recovery was partitioned between selection and complementarity effect. We are thus able for one community to look at aboveground biomass dynamic after and before disturbance in control and disturbed ecosystems and correspondig net biodiversity effect, selection effect and complementarity effect (figure \@ref(fig:gBEsingle)). Similarly to the aboveground biomass of the ecosystem, the net biodiversity effect and selection effect decrease following the disturbance, whereas the complementarity effect directly increases following the disturbance. Interestingly, we can see that this pattern of decrease of selection effect after disturbance and recovery after is similar to the effect of succession in forest early stages, when the new cohort arrives selection effect suddenly decreases and complementarity effect insure a small net effect (first century, sub-figure on left-bottom on figure \@ref(fig:gBEsingle)). Anyway the pattern is stronger after a disturbance, maybe due to an increased diversity allowing a stronger diversity effect.

```{r gBEsingle, fig.cap='Dynamic of complementarity and selection effects before and after the disturbance event for one ecosystem simulation including 125 species. Solid lines represents the mean value whereas areas represents the interval of values among simulations.'}
g <- BE %>% 
  select(sim, BE, time, agb) %>% 
  separate(sim, c("SR", "CHV", "disturbance"), remove = F) %>% 
  rbind(ecosystem %>% 
          mutate(BE = "ecosystem") %>%
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV", "disturbance"), remove = F)) %>% 
  rbind(BE_mature %>% 
          mutate(time = time - 600) %>% 
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV"), remove = F) %>% 
          mutate(disturbance = "0-75") %>% 
          separate_rows(disturbance, sep = "-", convert = T)) %>% 
  rbind(mature %>% 
          mutate(time = time-600) %>% 
          mutate(BE = "ecosystem") %>% 
          select(sim, BE, time, agb) %>% 
          separate(sim, c("SR", "CHV"), remove = F) %>% 
          mutate(disturbance = "0-75") %>% 
          separate_rows(disturbance, sep = "-", convert = T)) %>% 
  filter(SR == 125, disturbance %in% c(0,75), CHV == 10) %>% # 10, 3
  reshape2::dcast(SR + CHV + BE + time ~ disturbance, value.var = "agb") %>% 
  rename(control = `0`, disturbed = `75`) %>% 
  ggplot(aes(x = time, col = BE, group = BE)) +
  geom_line(aes(y = control, linetype = "control")) +
  geom_line(aes(y = disturbed, linetype = "disturbed")) + 
  xlab("Time (years)") + 
  ylab("Aboveground biomass (tonC/ha)") +
  scale_color_discrete("Biodiversity\neffect")
g0 <- g + 
  geom_line(aes(y = control, linetype = "control")) +
  geom_line(aes(y = disturbed, linetype = "disturbed")) + 
  geom_ribbon(aes(ymin = disturbed, ymax = control), 
              col = NA, fill = "lightgrey", alpha = 0.5)
gdist <- g + 
  geom_line(aes(y = control, linetype = "control"), lwd = 1.4) +
  geom_line(aes(y = disturbed, linetype = "disturbed"), lwd = 1.4) + 
  xlim(-10,100) + ylim(-30000, 40000) +
  scale_color_discrete(guide = F) +
  scale_linetype_discrete(guide = F)
gstart <- g + 
  geom_line(aes(y = control, linetype = "control"), lwd = 1.4) +
  geom_line(aes(y = disturbed, linetype = "disturbed"), lwd = 1.4) + 
  xlim(-600,-500) + ylim(-30000, 40000) +
  scale_color_discrete(guide = F) +
  scale_linetype_discrete(guide = F)
gridExtra::grid.arrange(g0, gstart, gdist, layout_matrix = rbind(c(1, 1), c(2, 3)))
```

@@

If we aggregate the result of all community with 125 species, we still observe the same pattern for all simulations compard to the single previous one (figure \@ref(fig:gBEunorm)). But due to an increase of biodiversity net effect through recovery time, complementarity importance in early recovery is less visible over a long period. Consequently normalizing by control biodiversity net effect can help avoiding this issue.

```{r gBEunorm, fig.cap='Dynamic of complementarity and selection effects for all ecosystems including 125 species. Solid lines represents the mean value whereas areas represents the range of values among simulations.'}
BE %>% 
  rbind(mutate(ecosystem, BE = "ecosystem")) %>% 
  left_join(., doe, by = 'sim') %>%
  filter(SR == 125, disturbance == 75) %>% 
  group_by(time, BE, disturbance, SR) %>%
  summarise(qt1 =quantile(agb, probs=0.05),
            qt2 =quantile(agb, probs=0.75),
            mean=mean(agb),
            n=n()) %>% 
  ggplot(aes(x = time)) +
  geom_ribbon(aes(ymin = qt1, ymax = qt2, fill = BE), alpha = 0.3) +
  geom_line(aes(y = mean, color = BE)) +
  xlab('Time (years)') +
  ylab('Aboveground biomass net effect')
```
